Make any stupid plot you want

### 2020-09-04 draft/intro.tex
latex + bulk notes in code

\documentclass[letterpaper,onecolumn,titlepage]{Ythesis}
\usepackage[utf8]{inputenc}
\usepackage{tikz}
\usepackage{array,multirow}
\usepackage{subcaption}
\usepackage{subfiles}
\usepackage{url}
\usepackage{amsmath}
\usepackage{float}
\usepackage{graphicx}
\graphicspath{{sections/figs/}{.figs/}}
\usepackage[backend=bibtex, style=numeric-comp]{biblatex}
\bibliography{glasslab_viz}

\title{Make any stupid plot you want}
\author{Hannah Aizenman}
\committee{Dr. Michael Grossberg (Advisor), Dr. Robert Haralick, Dr. Lev Manovich, Dr. Huy Vo}
\submitted{}
\abstract{Often the question in data exploration is not if a pattern occurs, but why. The search for the why is often the search for a conditionally dependent relationship in the dataset. While there are visualization methods that can be used to uncover a potential causal link between variables in the dataset, many of these techniques only work when the causal variables are categorical or can only be applied between two variables at a time or discard the complex, often spatiotemporal, structure of the dataset. Instead structure preserving methods for visualizing the distribution of observations provide a way of understanding some of the probabilistic relationships within and between the observations in these complex datasets. Using the type and structure of the variables in a dataset as a guide, this survey presents methods for visualizing conditional dependencies for multivariate datasets with discrete observations and visualizing probability distributions for datasets where observations are drawn from a continuous (functional) space. Because there is limited literature on explicit ways to visualize conditional dependency, we include techniques that suggest or can be adapted to show these dependencies.}

\begin{document}
\makefrontmatter

@@

>>>>

\documentclass[letterpaper,onecolumn,titlepage]{Ythesis}
\usepackage[utf8]{inputenc}
\usepackage{tikz}
\usepackage{array,multirow}
\usepackage{subcaption}
\usepackage{subfiles}
\usepackage{url}
\usepackage{amsmath}
\usepackage{float}
\usepackage{graphicx}
\graphicspath{{figures}{.figures}}
\usepackage[backend=bibtex, style=numeric-comp]{biblatex}
\bibliography{glasslab_viz}

\title{Make any stupid plot you want}
\author{Hannah Aizenman}
\committee{Dr. Michael Grossberg (Advisor), Dr. Robert Haralick, Dr. Lev Manovich, Dr. Huy Vo}
\submitted{}
\abstract{}
\begin{document}
\makefrontmatter

@@

\cite{bertinSemiologyGraphicsDiagrams2011}

\begin{figure}
    \includegraphics{figures/intro/munzner_datatypes}
    \label{fig:munzner_datatypes}
    \caption{Keys are unique lookup values used to find individual observations in the dataset. Keys are positional references, and can be coordinates on a map or unique values such as a primary key in a database or a (time, latitude, longitude) index in a data cube. Image modified from a diagram from Munzner's website\cite{munznerChDataAbstraction}}
\end{figure}

\cite{munznerWhatDataAbstraction2014}
